---
title: "R Notebook"
output: html_notebook
---

```{r}
library(RMySQL)
conn <- dbConnect(MySQL(),
                  user = "bigdata",
                  password = "mypassword",
                  dbname = "bigdata",
                  host = "bigdata.cdmore2v5bgl.us-east-1.rds.amazonaws.com")
result = dbSendQuery(conn, "SELECT * FROM Matches")
match = fetch(result, n = -1)
```


# loading the packages
```{r}
library(dplyr)
library(tidyverse)
```

# tidying the data

# subset the purchase_log
```{r}
match_number <- c(0:1000)
purchase <- subset(purchase_log, match_id %in% match_number)
match_subset <- subset(match, match_id %in% match_number)
```

# Add a new column called team_item for purchase dataset
```{r}
i <- 1
while (i < nrow(purchase) +1) {
  item <- purchase$item_id[i]
  row <- subset(item_ids, item_id == item)
  purchase$team_item[i] <- row$Team 
  i <- i + 1
}
```

# Change the player slot for purchase dataset
```{r}
purchase$player_slot[which(purchase$player_slot == 0)] <- 0
purchase$player_slot[which(purchase$player_slot == 1)] <- 0
purchase$player_slot[which(purchase$player_slot == 2)] <- 0
purchase$player_slot[which(purchase$player_slot == 3)] <- 0
purchase$player_slot[which(purchase$player_slot == 4)] <- 0
purchase$player_slot[which(purchase$player_slot == 128)] <- 1
purchase$player_slot[which(purchase$player_slot == 129)] <- 1
purchase$player_slot[which(purchase$player_slot == 130)] <- 1
purchase$player_slot[which(purchase$player_slot == 131)] <- 1
purchase$player_slot[which(purchase$player_slot == 132)] <- 1
```

# summary the purchase dataset
```{r}
purchase_time <- purchase
purchase_time$time[which(purchase_time$team_item == 0)] <- 0
```

```{r}
purchase_summary <- purchase_time %>%
  group_by(match_id, player_slot) %>%
  summarize(team_item = sum(team_item),
            average_time = mean(time))
purchase_summary
```

# subset the match dataset
```{r}
match_result <- match_subset[,c("match_id", "radiant_win")]
```

# mapping the summary of purchase into the match dataset
```{r}
i = 1
while (i < nrow(match_result)+1) {
  id <- match_result$match_id[i]
  rows <- subset(purchase_summary, match_id == id)
  match_result$radiant_teamitem[i] <- rows$team_item[which(rows$player_slot == 0)]
  match_result$dire_teamitem[i] <- rows$team_item[which(rows$player_slot == 1)]
  match_result$radiant_itemtime[i] <- rows$average_time[which(rows$player_slot == 0)]
  match_result$dire_itemtime[i] <- rows$average_time[which(rows$player_slot == 1)]
  i <- i+1
}
```

# calculating the diff
```{r}
match_result$item_diff <- match_result$radiant_teamitem - match_result$dire_teamitem
match_result$time_diff <- match_result$radiant_itemtime - match_result$dire_itemtime
```

# Data Visualization

# load the package
```{r}
library(ggplot2)
```

# item_diff vs. radiant_win
```{r}
ggplot(data = match_result, aes(x = radiant_win, y = item_diff)) +
  geom_boxplot() + 
  labs(title = "relationship between the difference of the team items and the final result",
       x = "The outcome",
       y = "The difference of the team items")
```

```{r}
ggplot(data = match_result, aes(x = radiant_win, y = time_diff)) +
  geom_boxplot() +
  labs(title = "relationship between the difference of the purchase time and the final result",
       x = "The outcome",
       y = "The difference of the purchase time")
```

# ANOVA
```{r}
match_result$radiant_win[which(match_result$radiant_win == "True")] <- 1
match_result$radiant_win[which(match_result$radiant_win == "False")] <- 0
```


```{r}
match_result
```

```{r}
model.lm <- lm(radiant_win ~ item_diff + time_diff,data = match_result)
summary(model.lm)
```

```{r}
model.aov <- aov(radiant_win ~ item_diff + time_diff,data = match_result)
summary(model.aov)
```


```{r}
model.aov <- aov(radiant_win ~ item_diff + time_diff, data = match_result)
summary(model.aov)
```

```{r}
model.radiant <- aov(radiant_win ~ radiant_teamitem + radiant_itemtime, data = match_result)
summary(model.radiant)
```


# SVM and prediction

# load package
```{r}
library(e1071)
```

# training set and testing set
```{r}
train <- sample(nrow(match_result),50)
train_set <- match_result[-train,]
test_set <- match_result[train,]
test_result <- test_set$radiant_win
```

# build the model
```{r}
model.log <- svm(radiant_win ~ item_diff + time_diff, data = train_set, kernel = "radial", cost=3.376,gamma=0.885)
```

```{r}
summary(model.log)
```

# prediction
```{r}
test <- test_set[,-2]
```
```{r}
test <- test[,c("time_diff","item_diff")]
```

```{r}
pred.log <- predict(model.log, test)
```

# Confusion Matrix
```{r}
table(pred.log,test_result)
```

# Accurate
```{r}
mean(pred.log == test_result)
```



# Chart view


```{r}
glimpse(chat)
```

```{r}
set.seed(100)
dota_chat <- sample_frac(chat, 1)
```

```{r}
library(tm)
library(wordcloud)
library(SnowballC)
```

```{r}
# First, we need to create a corpus.
dota_corpus <- tm::VCorpus(VectorSource(dota_chat$key))
# Next, we will convert the corpus to a plain text document.
dota_corpus <- tm::tm_map(dota_corpus, PlainTextDocument)

dota_corpus <- tm::tm_map(dota_corpus, removePunctuation)
# Then, we will remove all punctuation and stopwords.
# stopwords("english")
dota_corpus <- tm::tm_map(dota_corpus, function(x) removeWords(x, stopwords('english')))


dota_corpus <- tm_map(dota_corpus, stemDocument)
# This uses Dr. Martin Porter's stemming algorithm and the C libstemmer library generated by Snowball.
```

```{r}
dota_corpus
```



```{r}
wordcloud(dota_corpus, max.words = 100, random.order = FALSE,min.freq = 5)
```

